Networks Matter...or some nonsense like that

### 2016-11-25 amenIntro/amenIntro.Rmd
some updates

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

@@

* This is going to be a bit different than what is described in [Hoff's vignette](https://arxiv.org/pdf/1506.08237v1.pdf). 
      - As of this week, AMEN can now be estimated on networks where the actor composition changes over time, and to make that change we switch to using **lists** instead of **arrays**.
* In undirected longitudinal setting three inputs:
      - `Y`: a T length list of n x n adjacency matrices (see Table 2)
      - `Xdyad`: A T length list of n x n x p arrays
      - `Xrow`: A T length list of n x p matrices
* In directed longitudinal setting you can distinguish between:
      - Sender covariates `Xrow`
      - Receiver covariates `Xcol`

@@

```{r, echo=TRUE,eval=FALSE}
fit=ame_repL(Y=yL, Xdyad=xDyadL, Xrow=xNodeL, Xcol=NULL,
      nvar=TRUE, R=2,
      model="bin",symmetric=TRUE,
      burn=500,nscan=1000,odens=10, # WILL NEED TO BE LARGER
      plot=FALSE, print=FALSE, 
      seed=6886 # ALWAYS SET A SEED
      )
```

@@

## Out of sample model performance

* Code to perform this analysis for the example is shown in `git/netsMatter/code/example/runOutPerf.R`
* When we get out of sample results we will be evaluating across two metrics:
	- Receiver Operating Characteristic curves
	- Precision-Recall curves

@@

# Run amen in parallel
library(doParallel) ; library(foreach)
cl=makeCluster(4) ; registerDoParallel(cl)
foreach(ii=1:length(latDims), .packages=c("amen")) %dopar% {
	ameFit = ame_repL(
		Y=yL,Xdyad=xDyadL,Xrow=xNodeL,Xcol=NULL, model="bin",symmetric=TRUE,
		R=latDims[ii], 
		nscan=imps, seed=seed, burn=brn, odens=ods, 
		plot=FALSE, print=FALSE) 	
	save(ameFit, 
		file='~/Dropbox/netsMatter/replications/example/outputData/model_k',
			latDims[ii],'.rda')
}
stopCluster(cl)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

if(Sys.info()['user']=='janus829' | Sys.info()['user']=='s7m'){
	dropPath = '~/Dropbox/Research/netsMatter/replications/example/'
	gitPath = '~/Research/netsMatter/'
	dataPath = paste0(dropPath, 'inputData/')
	resultsPath = paste0(dropPath, 'outputData/') }
```

@@

* This is going to be a bit different than what is described in [Hoff's vignette](https://arxiv.org/pdf/1506.08237v1.pdf). 
      - As of yesterday, AMEN can now be estimated on networks where the actor composition changes over time, and to make that change we switch to using **lists** instead of **arrays**.
      	+ Hoff still need to give the new code a review.
* In undirected longitudinal setting three inputs:
      - `Y`: a T length list of n x n adjacency matrices (see Table 2)
      - `Xdyad`: A T length list of n x n x p arrays
      - `Xrow`: A T length list of n x p matrices
* In directed longitudinal setting you can distinguish between:
      - Sender covariates `Xrow`
      - Receiver covariates `Xcol`

@@

```{r, echo=TRUE,eval=FALSE}
fit=ame_repL(Y=yL, Xdyad=xDyadL, Xrow=xNodeL, Xcol=NULL,
      nvar=TRUE, R=2,
      model="bin",symmetric=TRUE,
      burn=500,nscan=1000,odens=10, 
      plot=FALSE, print=FALSE, 
      seed=6886 # ALWAYS SET A SEED
      )
```

@@

@@

# Run amen in parallel
library(doParallel) ; library(foreach)
cl=makeCluster(4) ; registerDoParallel(cl)
foreach(ii=1:length(latDims), .packages=c("amen")) %dopar% {
	ameFit = ame_repL(
		Y=yL,Xdyad=xDyadL,Xrow=xNodeL,Xcol=NULL, model="bin",symmetric=TRUE,
		R=latDims[ii], 
		nscan=imps, seed=seed, burn=brn, odens=ods, 
		plot=FALSE, print=FALSE) 	
	save(ameFit, 
		file=paste0('~/Dropbox/netsMatter/replications/example/outputData/model_k',
			latDims[ii],'.rda'))
}
stopCluster(cl)
```

## Might need parallelization...

* because we will want to assess how varying k changes GOF

```{r, echo=FALSE, fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
load(paste0(resultsPath, 'modelk1.rda')) ; fit1=fit
load(paste0(resultsPath, 'modelk2.rda')) ; fit2=fit
load(paste0(resultsPath, 'modelk3.rda')) ; fit3=fit
load(paste0(resultsPath, 'modelk4.rda')) ; fit4=fit

fits = list(fit1, fit2, fit3, fit4) ; names(fits) = paste0('k=',1:4)

gofSumm = do.call('rbind', lapply(1:length(fits), function(ii){
	fit = fits[[ii]]
	act = fit$GOF[1,-c(2:3)]
	gof = fit$GOF[-1,-c(2:3)]

	ggGof = melt(gof)[,-1]
	ggGof$act = act[match(ggGof$Var2, names(act))]	
	ggGof$K = names(fits)[ii]
	return(ggGof)
	}) )

ggplot(gofSumm, aes(x=value )) + 
	geom_histogram() + 
	geom_vline(aes(xintercept=act), color='red') + 
	facet_grid(Var2 ~ K) +
	theme(axis.text.x=element_text(angle=45,hjust=1))
```

## and to assess performance

* Code to perform this analysis for the example is shown in `git/netsMatter/code/example/runOutPerf.R`
* When we get out of sample results we will be evaluating across two metrics:
	- Sensitivity/Specificity & Precision/Recall

```{r, echo=FALSE}

source(paste0(gitPath, 'code/helpers/functions.R'))
source(paste0(gitPath, 'code/helpers/binPerfHelpers.R'))

load(paste0(resultsPath, 'model_k1_outPerfResults.rda'))
load(paste0(resultsPath, 'model_k2_outPerfResults.rda'))
load(paste0(resultsPath, 'model_k3_outPerfResults.rda'))
load(paste0(resultsPath, 'model_k4_outPerfResults.rda'))

preds = list(do.call('rbind', modsAme1), do.call('rbind', modsAme2), do.call('rbind', modsAme3), do.call('rbind', modsAme4))
names(preds) = paste0('k=',1:4)

aucSumm = do.call('rbind', 
	lapply(preds, function(x){ 
		cbind( 'AUC'=getAUC(x$prob, x$actual), 'AUC (PR)'=auc_pr(x$actual, x$prob) ) 
		} ) ) ; rownames(aucSumm) = names(preds)
aucSumm = aucSumm[order(aucSumm[,1],decreasing=TRUE),]
aucSumm = trim(format(round(aucSumm, 2), nsmall=2))
print( aucSumm )
```

## Issues

* Any missingness in covariates inputted into AME automatically get turned into 0 ... this is not good.
* We can get around this via imputing nodal and dyadic variables within AME
	- In this vein, I made a modified version of sbgcop that works over nodal and dyadic data...but we still need to incorporate this within the AME MCMC
	- also *within* because otherwise we'd have to run each model k times over different imputed datasets and use Rubin's rules to combine parameter estimates ... problematic especially when it comes to third order deps
* Computation time ... these models take a notable amount of time to converge
	- Mike's tower?
	- EC2 ... though the costs can build
